### 2021-11-23 documents/floats/ppekverbs.tex
regular verbs in data and docs
started cleaning up workflow

\begin{table}
\centering
\caption[Verbs preserving \gl{1}\gl{s_a_} \rc{w-} in \PPek]{Verbs preserving \gl{1}\gl{s_a_} \rc{w-} in \PPek \parencites[153, 200]{alves2017arara}[42, 80, 139, 209]{ikpengpacheco2001}[76, 130, 131, 137, 374, 397]{von1892bakairi}[68]{ikpengpacheco1997}[4; p.c., Angela Fabíola Alves Chagas]{meira2003bakairi}}
\label{tab:ppekverbs}
\begin{tabular}[t]{@{}lllll@{}}
\toprule
{} &          \PPek &          \arara &                       \ikpeng &        \bakairi \\
\midrule
\qu{say}     &    \rc{wɨ-ge-} &    \obj{wɨ-ge-} &                   \obj{ɨ-ge-} &     \obj{u-ge-} \\
\qu{bathe}   &    \rc{w-ipɨ-} &    \obj{w-ibɨ-} &     \obj{{\normalfont ∅}-ip-} &      \obj{w-i-} \\
\qu{be-1}    &     \rc{w-ap-} &     \obj{w-ap-} &                             – &      \obj{w-a-} \\
\qu{be-2}    &  \rc{w-et͡ʃi-} &  \obj{w-it͡ʃi-} &  \obj{{\normalfont ∅}-et͡ʃi-} &      \obj{w-i-} \\
\qu{come}    &    \rc{w-epɨ-} &    \obj{w-ebɨ-} &                 \obj{k-arep-} &   \obj{k-əewɨ-} \\
\qu{go down} &   \rc{w-ɨptə-} &  \obj{w-iptoŋ-} &  \obj{{\normalfont ?}-iptoŋ-} &  \obj{k-ɨtəgɨ-} \\
\qu{go}      &   \rc{w-ɨtən-} &    \obj{w-ɨdo-} &                 \obj{k-aran-} &     \obj{u-tə-} \\
\bottomrule
\end{tabular}
\end{table}

>>>>

\begin{table}
\centering
\caption[Verbs preserving \gl{1}\gl{s_a_} \rc{w-} in \PPek]{Verbs preserving \gl{1}\gl{s_a_} \rc{w-} in \PPek \parencites[153, 200]{alves2017arara}[76, 130, 131, 137, 374, 397]{von1892bakairi}[42, 80, 139, 209]{ikpengpacheco2001}[68]{ikpengpacheco1997}[4; p.c., Angela Fabíola Alves Chagas]{meira2003bakairi}}
\label{tab:ppekverbs}
\begin{tabular}[t]{@{}lllll@{}}
\mytoprule
{} &          \PPek &          \arara &                       \ikpeng &        \bakairi \\
\midrule
\qu{be-1}    &     \rc{w-ap-} &     \obj{w-ap-} &                             – &      \obj{w-a-} \\
\qu{be-2}    &  \rc{w-et͡ʃi-} &  \obj{w-it͡ʃi-} &  \obj{{\normalfont ∅}-et͡ʃi-} &      \obj{w-i-} \\
\qu{say}     &    \rc{wɨ-ge-} &    \obj{wɨ-ge-} &                   \obj{ɨ-ge-} &     \obj{u-ge-} \\
\qu{go}      &   \rc{w-ɨtən-} &    \obj{w-ɨdo-} &                 \obj{k-aran-} &     \obj{u-tə-} \\
\qu{come}    &    \rc{w-epɨ-} &    \obj{w-ebɨ-} &                 \obj{k-arep-} &   \obj{k-əewɨ-} \\
\qu{go down} &   \rc{w-ɨptə-} &  \obj{w-iptoŋ-} &  \obj{{\normalfont ?}-iptoŋ-} &  \obj{k-ɨtəgɨ-} \\
\qu{bathe}   &    \rc{w-ipɨ-} &    \obj{w-ibɨ-} &     \obj{{\normalfont ∅}-ip-} &      \obj{w-i-} \\
\bottomrule
\end{tabular}
\end{table}

### 2021-11-23 documents/floats/ptirverbs.tex
regular verbs in data and docs
started cleaning up workflow

\begin{table}
\centering
\caption[Verbs preserving \gl{1}\gl{s_a_} \rc{w-} in \PTir]{Verbs preserving \gl{1}\gl{s_a_} \rc{w-} in \PTir \parencites[292, 294, 339]{triomeira1999}[112, 113, 114, 115, 165]{meira1998proto}}
\label{tab:ptirverbs}
\begin{tabular}[t]{@{}llll@{}}
\toprule
{} &          \PTir &          \trio &                     \akuriyo \\
\midrule
\qu{go}   &  \rc{wɨ-təmɨ-} &  \obj{wɨ-tən-} &                \obj{ə-təmɨ-} \\
\qu{say}  &    \rc{wɨ-ka-} &   \obj{wɨ-ka-} &                 \obj{wɨ-ka-} \\
\qu{come} &  \rc{w-əʔepɨ-} &  \obj{w-əepɨ-} &  \obj{{\normalfont ∅}-eepɨ-} \\
\qu{be-1} &      \rc{w-a-} &     \obj{w-a-} &     \obj{{\normalfont ∅}-a-} \\
\qu{be-2} &    \rc{w-eʔi-} &    \obj{w-ei-} &   \obj{{\normalfont ?}-eʔi-} \\
\bottomrule
\end{tabular}
\end{table}

>>>>

\begin{table}
\centering
\caption[Verbs preserving \gl{1}\gl{s_a_} \rc{w-} in \PTir]{Verbs preserving \gl{1}\gl{s_a_} \rc{w-} in \PTir \parencites[112, 113, 114, 115, 165]{meira1998proto}[292, 294, 339]{triomeira1999}}
\label{tab:ptirverbs}
\begin{tabular}[t]{@{}llll@{}}
\mytoprule
{} &          \PTir &          \trio &                     \akuriyo \\
\midrule
\qu{be-1} &      \rc{w-a-} &     \obj{w-a-} &     \obj{{\normalfont ∅}-a-} \\
\qu{be-2} &    \rc{w-eʔi-} &    \obj{w-ei-} &   \obj{{\normalfont ?}-eʔi-} \\
\qu{say}  &    \rc{wɨ-ka-} &   \obj{wɨ-ka-} &                 \obj{wɨ-ka-} \\
\qu{go}   &  \rc{wɨ-təmɨ-} &  \obj{wɨ-tən-} &                \obj{ə-təmɨ-} \\
\qu{come} &  \rc{w-əʔepɨ-} &  \obj{w-əepɨ-} &  \obj{{\normalfont ∅}-eepɨ-} \\
\bottomrule
\end{tabular}
\end{table}

### 2021-11-23 documents/floats/pwaireg.tex
started cleaning up workflow

\begin{table}
\centering
\caption[Regular \PWai verbs]{Regular \qu{to fall} (\gl{s_a_}) and \qu{to sleep} (\gl{s_p_}) in \PWai \parencites[150]{howard2001wrought}[209, 211]{hawkins1953waiwai}[189, 190, 196]{hixkaryanaderby1985}[30]{waiwaihawkins1998}}
\label{tab:pwaireg}
\begin{tabular}[t]{@{}lllllll@{}}
\mytoprule
{} & \multicolumn{2}{l}{\PWai} & \multicolumn{2}{l}{\hixka} & \multicolumn{2}{l}{\waiwai} \\
{} &    \qu{to fall} &     \qu{to sleep} &     \qu{to fall} &   \qu{to sleep} &       \qu{to fall} &      \qu{to sleep} \\
\midrule
\gl{1}   &  \rc{k-eɸurka-} &   \rc{kɨ-wɨnɨkɨ-} &  \obj{k-ehurka-} &  \obj{kɨ-nɨkɨ-} &    \obj{k-eɸɨrka-} &   \obj{kɨ-wɨnɨkɨ-} \\
\gl{2}   &  \rc{m-eɸurka-} &    \rc{o-wɨnɨkɨ-} &  \obj{m-ehurka-} &  \obj{o-wnɨkɨ-} &    \obj{m-eɸɨrka-} &   \obj{mɨ-wɨnɨkɨ-} \\
\gl{1+2} &  \rc{t-eɸurka-} &  \rc{tɨt-wɨnɨkɨ-} &  \obj{t-ehurka-} &  \obj{tɨ-nɨkɨ-} &  \obj{t͡ʃ-eɸɨrka-} &  \obj{tɨt-wɨnɨkɨ-} \\
\gl{3}   &  \rc{ɲ-eɸurka-} &   \rc{nɨ-wɨnɨkɨ-} &  \obj{ɲ-ehurka-} &  \obj{nɨ-nɨkɨ-} &    \obj{ɲ-eɸɨrka-} &   \obj{nɨ-wɨnɨkɨ-} \\
\bottomrule
\end{tabular}
\end{table}

>>>>

\begin{table}
\centering
\caption[Regular \PWai verbs]{Regular \qu{to fall} (\gl{s_a_}) and \qu{to sleep} (\gl{s_p_}) in \PWai \parencites[30]{waiwaihawkins1998}[189, 190, 196]{hixkaryanaderby1985}[150]{howard2001wrought}[209, 211]{hawkins1953waiwai}}
\label{tab:pwaireg}
\begin{tabular}[t]{@{}lllllll@{}}
\mytoprule
{} & \multicolumn{2}{l}{\PWai} & \multicolumn{2}{l}{\hixka} & \multicolumn{2}{l}{\waiwai} \\
{} &    \qu{to fall} &     \qu{to sleep} &     \qu{to fall} &   \qu{to sleep} &       \qu{to fall} &      \qu{to sleep} \\
\midrule
\gl{1}   &  \rc{k-eɸurka-} &   \rc{kɨ-wɨnɨkɨ-} &  \obj{k-ehurka-} &  \obj{kɨ-nɨkɨ-} &    \obj{k-eɸɨrka-} &   \obj{kɨ-wɨnɨkɨ-} \\
\gl{2}   &  \rc{m-eɸurka-} &    \rc{o-wɨnɨkɨ-} &  \obj{m-ehurka-} &  \obj{o-wnɨkɨ-} &    \obj{m-eɸɨrka-} &   \obj{mɨ-wɨnɨkɨ-} \\
\gl{1+2} &  \rc{t-eɸurka-} &  \rc{tɨt-wɨnɨkɨ-} &  \obj{t-ehurka-} &  \obj{tɨ-nɨkɨ-} &  \obj{t͡ʃ-eɸɨrka-} &  \obj{tɨt-wɨnɨkɨ-} \\
\gl{3}   &  \rc{ɲ-eɸurka-} &   \rc{nɨ-wɨnɨkɨ-} &  \obj{ɲ-ehurka-} &  \obj{nɨ-nɨkɨ-} &    \obj{ɲ-eɸɨrka-} &   \obj{nɨ-wɨnɨkɨ-} \\
\bottomrule
\end{tabular}
\end{table}

### 2021-11-23 documents/floats/pwaiverbs.tex
fixed proto-pekodian 'to go'
regular verbs in data and docs
started cleaning up workflow

\begin{table}
\centering
\caption[Verbs preserving \gl{1}\gl{s_a_} \rc{w-} in \PWai]{Verbs preserving \gl{1}\gl{s_a_} \rc{w-} in \PWai \parencites[4]{hixkaryanaderby1979}[71, 85]{waiwaihawkins1998}[70, 197, 198; p.c., Spike Gildea]{hixkaryanaderby1985}}
\label{tab:pwaiverbs}
\begin{tabular}[t]{@{}llll@{}}
\toprule
{} &        \PWai &        \hixka &         \waiwai \\
\midrule
\qu{say}  &  \rc{wɨ-ka-} &   \obj{ɨ-ka-} &    \obj{wɨ-ka-} \\
\qu{be-1} &   \rc{w-ah-} &   \obj{w-ah-} &      \obj{w-a-} \\
\qu{be-2} &  \rc{w-eʃi-} &  \obj{w-eʃe-} &   \obj{w-eeʃi-} \\
\qu{go}   &  \rc{wɨ-to-} &   \obj{ɨ-to-} &  \obj{kɨw-tom-} \\
\bottomrule
\end{tabular}
\end{table}

>>>>

\begin{table}
\centering
\caption[Verbs preserving \gl{1}\gl{s_a_} \rc{w-} in \PWai]{Verbs preserving \gl{1}\gl{s_a_} \rc{w-} in \PWai \parencites[70, 197, 198]{hixkaryanaderby1985}[4]{hixkaryanaderby1979}[71, 85; p.c., Spike Gildea]{waiwaihawkins1998}}
\label{tab:pwaiverbs}
\begin{tabular}[t]{@{}llll@{}}
\mytoprule
{} &         \PWai &        \hixka &         \waiwai \\
\midrule
\qu{be-1} &    \rc{w-ah-} &   \obj{w-ah-} &      \obj{w-a-} \\
\qu{be-2} &   \rc{w-eʃi-} &  \obj{w-eʃe-} &   \obj{w-eeʃi-} \\
\qu{say}  &   \rc{wɨ-ka-} &   \obj{ɨ-ka-} &    \obj{wɨ-ka-} \\
\qu{go}   &  \rc{wɨ-tom-} &   \obj{ɨ-to-} &  \obj{kɨw-tom-} \\
\bottomrule
\end{tabular}
\end{table}
